Comparison of Catalogs

### 2024-07-25 compare/compare.qmd
rel diff + log a26

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support
#quantity_support()
from astropy.stats import sigma_clip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    try:
        x_data = np.ma.array(x.value, mask=np.isnan(x.value))
        y_data = np.ma.array(y.value, mask=np.isnan(y.value))
        # initialize a linear fitter
        fit = fitting.LinearLSQFitter()

@@

@@

```
As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

## Inclanation
```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```
## Major Axis

```{python}
scatter_plot(dt["a26_1"], dt["R1"], logscale = True)
```

>>>>

```{python}
#| echo: false
import numpy as np
import matplotlib.pyplot as plt
from sklearn.metrics import r2_score
from astropy.io import ascii
from astropy.coordinates import SkyCoord
from astropy.table import Table, join, QTable
import astropy.units as u
from astropy.visualization import quantity_support, hist
#quantity_support()
from astropy.stats import sigma_clip
from astropy.modeling import models, fitting
from scipy.stats import pearsonr
import seaborn as sns
import pandas as pd
import glob
import os
plt.style.use('ggplot')

@@

    Returns:
    tuple: A tuple containing the following elements:
        - slope (float): The slope of the fitted linear model.
        - intercept (float): The intercept of the fitted linear model.
        - r2 (float): The R-squared value, indicating the proportion of variance explained by the linear model.
        - corr (float): The Pearson correlation coefficient, measuring the linear correlation between x and y.
    """
    try:
        x_data = np.ma.array(x.value, mask=np.isnan(x.value)&x.mask)
        y_data = np.ma.array(y.value, mask=np.isnan(y.value))
        # initialize a linear fitter
        fit = fitting.LinearLSQFitter()

@@

- Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.

$$\text{Percentage change} = \frac{V_{Hecate} - V_{LCV}}{V_{Hecate}}\cdot 100 \%$$

```{python}
def relative_diff(hec, lcv):
    diff = 100*(hec - lcv) / hec
    diff[np.isinf(diff)] = np.nan
    return diff
```

@@

```
**Percentage change:**
```{python}
dt["diff_T"] = relative_diff(dt["T"], dt["TType"])
dt["diff_T"].info("stats")
```
```{python}
sns.distplot(dt["diff_T"])
plt.xlabel("Percentage change of Types of Galaxies")
plt.show()
```
As we can see we don't have any significant correlation between the Types of galaxies and thus the correlation of the inclanations are 0

## Inclanation
```{python}
scatter_plot(dt["inc"], dt["INCL"], sigma =True)
```

```{python}
dt["diff_inc"] = relative_diff(dt["INCL"], dt["inc"])
dt["diff_inc"].info("stats")
```
```{python}
sns.distplot(dt["diff_inc"])
plt.xlabel("Percentage change of the inclination of the galaxies [%]")
plt.show()
```

## Major Axis

```{python}
scatter_plot(dt["a26_1"], dt["R1"])
```
it is not very clear if we truly have a correlation or not. We need to see the linear correlation of the decimal logarithms.

```{python}
dt["log_a26"] = np.log(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
dt["log_R1"].info
```
```{python}
scatter_plot(dt["log_a26"], dt["log_R1"], sigma = True)
```
